Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/results.tex
done editing approach and results. Some additional examples may be needed

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history from May 2011 to June 2012, which contains 6,605 changes and 72,484 comments.

\subsection{Data Preparation}
We used the commit messages and comments in the dataset.
Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.

@@

To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
We also determined the effectiveness of our approach using bootstrapping cross validation.

@@

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model. The comments drawn in the green area are those satisfied condition of useful model, and the comments drawn in the red area are those satisfied condition of useless, while the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}). 
The total number of comments from this classification results is described in Table \ref{tb:classify_number}.

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set drawn in this area.
Similarly, majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set (\texttt{YES} = 3) adhere in the top left of the graph
while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
However, the unclear set still spread out over the graph.
Therefore, we cannot determine relationship between their similarity values.

There is an overlap section as shown in Fig. \ref{fig:scatter}.
This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
This means that the erroneous overlapping section is relatively small.
Excluding the overlaping classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to investigate for usefulness classification.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give an average performance of our models.
For a baseline, we also determined the performance of the random classifier using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, our models also achieved higher results than the random models twice for both precision and recall.

@@

According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random  classifier.}

@@

Automatic systems are generally known for saving human effort and also reduce human errors.
We analyze the results to determine the performance of our models.
In addition, we also consider scalability of our models as it only validated in the small set of comments.
% \pick{Trying to explain why we considering this}

\textbf{Cost Efficiency:}
% briefly explain
We determined cost efficiency in terms of time use for manual assessment.
For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
However, this time can be inaccurate since practitioners did not assess under the controlled environment.

>>>>

Our case study uses the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history from May 2011 to June 2012, which contains 6,605 changes and 72,484 comments.

\subsection{Data Preparation}
We use the commit messages and comments within Gerrit as our data set.
Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated e.e. bot messages.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples. In practice, they are not considered in a code review  and are not substantively relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). These are easily detected by their automatically generated signature 
e.g. XXX 
\dan{good example here} 
Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are XXX
\dan{good example here} 
This leaves us only human-written comments that cannot automatically be classified as useless.

@@

\subsection{Manual Comment Usefulness Assessment}
In this case study, three participants (the first two authors and one student) independently assessed comment usefulness by addressing the question, ``Is this comment directly useful for approving or modifying the change request?''
Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
From the voting scores, we regarded comments with three \texttt{YES} votes as \emph{useful} comments, and comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \emph{useless} comments. For the comments with one and two \texttt{YES} votes, we defined them to have \emph{unclear} usefulness.

@@

To answer this question, we randomly sampled 318 comments from our data set and manually assessd their usefulness.
Then, we used these comments for both training and test data for our approach to determine its effectiveness.
We also determined the confidence in the effectiveness estimates using bootstrapping cross validation to estimate variability in the performance measures due to using sample data.

@@

To determine similarity and dissimilarity thresholds for our model, we iterated $S_t$ and $D_t$ values from every unique similarity and dissimilarity value in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on maximizing the F1-measure score.
The models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85 were useless (\texttt{YES} = 0),  111 were unclear (\texttt{YES} = 1 or 2), and 122 were useful (\texttt{YES} = 3). The precision and recall were 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.

Figure \ref{fig:scatter} shows the relationship between usefulness classes from our model and comment sets from manual assessment. 
The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model. The comments drawn in the green area are those that satisfied the condition for useful comments, and the comments drawn in the red area are those satisfied the useless condition, while the comments drawn in the white area are those not satisfied any condition (i.e. \emph{undetermined}) and hence remain unclassified. 
The total number of comments from this classification results is described in Table \ref{tb:classify_number}.

%%Interpret: comments & model%%%%
Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set fall in this area.
Similarly, the majority of comments drawn in the red area are comments from the useless set.
It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
Most comments from the useful set (\texttt{YES} = 3) are in the top left of the graph
while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
However, the unclear set still spread out over the similarity intervals and therefore we cannot determine 
a relationship with their similarity values. That is, we have no evidence to support that the undetermined set corresponds unclear comments and hence undetermined is not a useful classification.

There is an overlap section shown in Fig. \ref{fig:scatter}.
This is a conflict between the two classification conditions where a comment satisfies both simultaneously.  
This phenomenon can occur since similarity and dissimilarity threshold values of each group are ``fuzzy" and both models tend to maximize coverage of classification. Also similarity and dissimilarity are discreet and subject to some degree of granularity issues 
However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
In more extended experiments, less than 2\% were in the overlap set and this contradictory classification is relatively small.
Excluding the overlap classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our model suggesting that there are likely other indicators different from similarity that determine usefulness.

@@

\textbf{Validation:}
We validated our approach using bootstrapping cross validation. By validation be mean to estimate the variability in the estimate of the 
performance measures from the training set to indicate how a accurate these are for the method in general.
We randomly selected 90\% of 318 comments for training set and determine thresholds.
The constructed model is then applied on the remaining 10\% comments as the validation set.
The precision, recall and F-measure scores are measured and recorded.
This validation was repeated 300 times to give the average and standard deviation for these performance measures. Bootstrapping is 
used because of concern about our relatively small sample size and possibly instability in using customary Jackknifing cross-validation.
For a baseline comparison, we also determined the performance of a random classifier (i.e. places items in classes with equal probability) using the same methods.

Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures e.g. mean Precision for Useless is notably higher than Random with about the same standard deviation so it's clearly significant.

@@

According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}

@@

Automatic systems are generally known for saving human effort and also reduce errors.
We analyze the results to determine the performance of our models.
In addition, we also consider scalability of our models as it only validated for small numbers of comments. The concern is that the model may behave poorly at larger scale possibly leaving more manual assessment effort than is saved through using the method. 
% \pick{Trying to explain why we considering this}

\textbf{Cost Efficiency:}
% briefly explain
We determined cost efficiency in terms of time use for manual assessment.
For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.
